---
title: "Infectious Diseases"
author: "Charles Martinez (cmm5627), Happy Situ (hys82), Jenna Webb (jnw653)"
date: "October 23, 2015"
output: html_document
---

For this project, we found a set of data that listed cases of different infectious dieases in various counties in California, as well as the total population of each county. It included how many males and females were infected per year, as well as the total number of infections per county per year.   


Here is a summary of our data:  

```{r, echo = FALSE}
source("../01 Data/InfectiousDiseases.R")
summary(diseases)
```

Here is a subset of our data:  
```{r}
head(diseases)
```

###Scatter Plot:  

###Crosstab with a KPI and Parameters:  
This is the code used to generate the crosstab:
```
require("jsonlite")
require("RCurl")
require("ggplot2")

KPI_Very_Low_value = 0
KPI_Low_value = 10
KPI_Medium_value = 100

df <- data.frame(fromJSON(getURL(URLencode(gsub("\n", " ", '129.152.144.84:5001/rest/native/?query=
"select SEX, County, kpi, 
case
when kpi <= "p1" then \\\'Very Low\\\'
when kpi <= "p2" then \\\'Low\\\'
when kpi <= "p3" then \\\'Medium\\\'
else \\\'High\\\'
end kpi
from (select SEX, County, COUNT, 
avg(Count) kpi
from INFECTIOUS_DISEASES
group by SEX, County, COUNT)
order by County;"
')),httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521/PDBF15DV.usuniversi01134.oraclecloud.internal', USER='cs329e_jnw653', PASS='orcl_jnw653', MODE='native_mode', MODEL='model', returnDimensions = 'False', returnFor = 'JSON', p1=KPI_Very_Low_value, p2=KPI_Low_value, p3=KPI_Medium_value), verbose = TRUE)))



ggplot() + 
  coord_cartesian() + 
  scale_x_discrete() +
  scale_y_discrete() +
  labs(title='TITIIELLELLE') +
  labs(x=paste("SEX"), y=paste("County")) +
  layer(data=df, 
        mapping=aes(x=SEX, y=COUNTY, label=COUNTY), #label is wrong here
        stat="identity", 
        stat_params=list(), 
        geom="text",
        geom_params=list(colour="black"), 
        position=position_identity()
  ) +
  layer(data=df, 
        mapping=aes(x=SEX, y=COUNTY, label=COUNTY), #label is wrong here
        stat="identity", 
        stat_params=list(), 
        geom="text",
        geom_params=list(colour="black", vjust=4), 
        position=position_identity()
  ) 
```
```{r}
source("../03 R SQL Visualizations/Crosstab_jnw.R", echo = TRUE)
```

###Bar Chart with Reference Lines:  
